### 2020-12-22 README.Rmd
github action attempt plus *removal of tidyr 0.8.3 coverage*

<!-- badges: start -->
[![R-CMD-check, code coverage, pkgdown site creation](https://github.com/skgallagher/EpiCompare/workflows/R-CMD-check,%20code%20coverage,%20pkgdown%20site%20creation/badge.svg)](https://github.com/skgallagher/EpiCompare/actions)
<!-- [![Travis build status](https://travis-ci.org/skgallagher/EpiCompare.svg?branch=master)](https://travis-ci.org/skgallagher/EpiCompare) -->
[![codecov](https://codecov.io/gh/skgallagher/EpiCompare/branch/master/graph/badge.svg)](https://codecov.io/gh/skgallagher/EpiCompare)

@@

1. For writing code that works with `tidyverse` 1.0 vs `tidyverse` <= 0.8.3. We followed ideas found in [tidyr: in-packages](https://tidyr.tidyverse.org/articles/in-packages.html), for the code, and - when working with Travis CI (using a matrix for multiple builds) - we leverage ideas in [tidyverse travis on github](https://github.com/tidyverse/design/issues/95) and [tidyverse principles](https://principles.tidyverse.org/changes-multivers.html).
2. For writing your own `geom`s and `stat`s that works with `ggtern` (which are generally restricted), the following 2 stack-exchange articles helped use do so with ease:
    a. [stack-exchange: personal code idea](https://stackoverflow.com/questions/57175114/ternary-plot-scaling-opacity-across-groups)
    b. [stack-exchange: being able to access ggtern's element write away](https://stackoverflow.com/questions/31589479/how-to-fix-no-item-called-packagepkg-on-the-search-list-without-using-libra#comment51172891_31589479)

>>>>

<!-- badges: start -->
[![R-CMD-check, code coverage](https://github.com/skgallagher/EpiCompare/workflows/R-CMD-check,%20code%20coverage/badge.svg)](https://github.com/skgallagher/EpiCompare/actions)
<!-- [![Travis build status](https://travis-ci.org/skgallagher/EpiCompare.svg?branch=master)](https://travis-ci.org/skgallagher/EpiCompare) -->
[![codecov](https://codecov.io/gh/skgallagher/EpiCompare/branch/master/graph/badge.svg)](https://codecov.io/gh/skgallagher/EpiCompare)

@@

1. For writing code that works with `tidyverse` 1.0 vs `tidyverse` <= 0.8.3. We followed ideas found in [tidyr: in-packages](https://tidyr.tidyverse.org/articles/in-packages.html), for the code, and - when working with Travis CI (using a matrix for multiple builds) - we leverage ideas in [tidyverse travis on github](https://github.com/tidyverse/design/issues/95) and [tidyverse principles](https://principles.tidyverse.org/changes-multivers.html). **This is no longer done (was removed 22 December 2020), as the rest of `tidyrverse` has moved on and now requires `tidyr >1.0.0`.
2. For writing your own `geom`s and `stat`s that works with `ggtern` (which are generally restricted), the following 2 stack-exchange articles helped use do so with ease:
    a. [stack-exchange: personal code idea](https://stackoverflow.com/questions/57175114/ternary-plot-scaling-opacity-across-groups)
    b. [stack-exchange: being able to access ggtern's element write away](https://stackoverflow.com/questions/31589479/how-to-fix-no-item-called-packagepkg-on-the-search-list-without-using-libra#comment51172891_31589479)
